\vspace{-.2in} Squint: Lossy Hierarchical Compression on Symbol Streams \vspace{-.1in}

### 2012-12-12 tex/paper.tex
Bugfix

The second piece of text is one of the entries to this year's International
Obfuscated C code contest, at \url{http://www.ioccc.org/2012/deckmyn/deckmyn.c}
. We believe this is a particularly good example since its structure is foreign,
but still discernable. Whitespace is particularly important in standard english
but our lossifiers don't treat it any differently from any other symbol.
The size of the lossified grammar is 1576 compared with the original size of
1973. The intricate whitespacing was lost, but the clear delineation into
sections was kept, key words such as `define' and `for' are very visible, and
the texture of the obfuscated C is very obvious. For instance, after the
distinct `#define' headers, the first sections has a bunch of control statements
like `for' and `if', while the middle sections have very generous spacing
and many repeated pointer derence operators such as `***'. Both of these
kinds of textures are retained after lossifying.

>>>>

The second piece of text is one of the entries to this year's International
Obfuscated C code contest, at \url{http://www.ioccc.org/2012/deckmyn/deckmyn.c}
. We believe this is a particularly good example since its structure is
foreign, but still discernable. Whitespace is particularly important in
standard english but our lossifiers don't treat it any differently from any
other symbol.  The size of the lossified grammar is 1576 compared with the
original size of 1973. The intricate whitespacing was lost, but the clear
delineation into sections was kept, key words such as `define' and `for' are
very visible, and the texture of the obfuscated C is very obvious. For
instance, after the distinct `\#define' headers, the first sections has a bunch
of control statements like `for' and `if', while the middle sections have very
generous spacing and many repeated pointer derence operators such as `***'.
Both of these kinds of textures are retained after lossifying.
